% Common Prayers
\newcommand{\glory}{Glory to the Father, and to the Son, and to the Holy Spirit}%
\newcommand{\bothnow}{Both now and forever, and to the ages of ages}%
\newcommand{\glorybothnow}{\glory; \bothnow. Amen. }%
\newcommand{\mercy}[1]{Lord, have mercy. \alt{(x#1)} }%
\newcommand{\throughtheprayers}{Through the prayers of our holy fathers, Lord Jesus Christ, our God, have mercy on us. Amen.}%
\newcommand{\alleluia}{Alleluia, Alleluia, Alleluia. Glory to you, O God. \alt{(x3)}}%

\newcommand{\ourfather}{%
	Our Father, in heaven, may your name be hallowed; your kingdom come;
	your will be done on earth as in heaven. Give us today our daily bread,
	and forgive us our debts, as we forgive our debtors. And do not lead
	us into temptation, but deliver us from the evil one.
}%

\newcommand{\heavenlyking}{%
  Heavenly King, Paraclete, Spirit of Truth, present everywhere, filling all things,
  Treasury of blessings and Giver of life, come and dwell in us,
  cleanse us from every stain, and, O Good One, save our souls.
}%

\newcommand{\trisagion}{%
	Holy God, Holy Strong, Holy Immortal, have mercy on us. \alt{(x3)}

	\glorybothnow

	All-holy Trinity, have mercy on us. Lord, cleanse us from our sins.
	Master, pardon our iniquities. Holy One, visit and heal our infirmities
	for your name's sake.

	\mercy{3}

	\glorybothnow

	\ourfather

  \throughtheprayers
}%

\newcommand{\comeletusworship}{%
  \mercy{12}

  \glorybothnow

  Come, let us worship and fall down before the King, our God.

  Come, let us worship and fall down before Christ, the King, our God.

  Come, let us worship and fall down before Christ himself, the King, our God.
}%

\newcommand{\greaterinhonour}{%
  Greater in honour than the Cherubim and beyond compare more glorious than the Seraphim,
  without corruption you gave birth to God the Word; truly the Mother of God, we magnify you.
}%

\newcommand{\creed}{%
  I believe in one God, Father almighty, maker of heaven and earth, of all things visible and invisible.
  And in one Lord Jesus Christ, the only-begotten Son of God, begotten from the Father before all ages.
  Light from Light, true God from true God, begotten not made, consubstantial with the Father;
  through him all things were made; for our sake and for our salvation came down from heaven,
  and was incarnate from the Holy Spirit and the Virgin Mary and became man;
  he was crucified also for us under Pontius Pilate,
  and suffered and was buried; he rose again on the third day, in accordance with the Scriptures,
  and ascended into heaven and is seated at the right hand of the Father;
  he is coming again in glory to judge the living and the dead; and his kingdom will have no end.
  And in the Holy Spirit, the Lord, the Giver of life, who proceeds from the Father,
  who together with the Father and the Son is worshipped and together glorified; who spoke through the Prophets.
  In one, Holy, Catholic and Apostolic Church; I confess one Baptism for the forgiveness of sins.
  I await the resurrection of the dead and the life of the age to come. Amen.
}%

\newcommand{\hours}{%
  At every time and at every hour, in heaven and on earth worshipped and glorified,
  Christ God, long-suffering, great in mercy, great in compassion,
  loving the just and merciful to sinners, calling all to salvation by the promise of the blessings to come;
  do you, Lord, yourself accept our entreaties at this hour, and direct our lives to your commandments.
  Sanctify our souls, purify our bodies, correct our thoughts,
  cleanse our ideas and deliver us from every distress, evil, and pain.
  Wall us about with your holy Angels, that,
  protected and guided by their host, we may reach the unity of the faith and the knowledge of your unapproachable glory;
  for you are blessed to the ages of ages. Amen.
}

\newcommand{\grantlord}[1]{% First argument is the time of day.
  Grant, Lord, this #1 to keep us without sin.
  Blessed are you, Lord, the God of our fathers, and praised and glorified is your name for evermore. Amen.
  May your mercy, Lord, be upon us, as we have trusted in you.
  Blessed are you, Lord, teach me your statutes.
  Blessed are you, Master, make me understand your statutes.
  Blessed are you, Holy One, enlighten me with your statutes.
  Lord, your mercy is for ever: Do not scorn the work of your hands.
  To you praise is due, to you song is due, to you glory is due,
  Father, Son, and Holy Spirit, now and for ever, and to the ages of ages. Amen.
}%

\newcommand{\smalldoxology}[1]{% First argument is the time of day.
  Glory to God in the highest, and on earth peace, goodwill among men.
  We praise you, we bless you, we worship you, we glorify you, we give you thanks for your great glory.
  Lord, King, God of heaven, Father almighty: Lord, only-begotten Son, Jesus Christ and Holy Spirit.
  Lord God, Lamb of God, Son of the Father, who take away the sin of the world, have mercy on us;
  you take away the sins of the world. 
  Receive our prayer, you who sit on the right hand of the Father, and have mercy on us.
  For you alone are holy, you alone are Lord, Jesus Christ, to the glory of God the Father. Amen.\rest

  Every evening I will bless you, and praise your name for ever and to the ages of ages.
  Lord, you have been our refuge from generation to generation.
  I said, Lord, have mercy on me, heal my soul, for I have sinned against you.
  Lord, I have run to you for refuge; teach me to do your will for you are my God.
  For with you is the source of life, and in your light we shall see light.
  Continue your mercy towards those who know you.\rest

  \grantlord{#1}
}

\newcommand{\psalmfifty}{%
    Have mercy on me, O God, in accordance with your great mercy.
    According to the multitude of your compassion blot out my offence.
    Wash me thoroughly from my wickedness, and cleanse me from my sin.
    For I acknowledge my wickedness, and my sin is ever before me.
    Against you alone I have sinned and done what is evil in your sight,
    that you may be justified in your words and win when you are judged.
    For see, in wickedness I was conceived and in sin my mother bore me.
    For see, you have loved truth; you have shown me the hidden and secret things of your wisdom.
    You will sprinkle me with hyssop and I shall be cleansed.
    You will wash me and I shall be made whiter than snow.
    You will make me hear of joy and gladness; the bones which have been humbled will rejoice.
    Turn away your face from my sins and blot out all my iniquities.
    Create a clean heart in me, O God, and renew a right Spirit within me.
    Do not cast me out from your presence, and do not take your Holy Spirit from me.
    Give me back the joy of your salvation, and establish me with your sovereign Spirit.
    I will teach transgressors your ways, and sinners will turn to you again.
    O God, the God of my salvation, deliver me from bloodshed and my tongue will rejoice at your justice.
    Lord, you will open my lips, and my mouth will proclaim your praise.
    For if you had wanted a sacrifice, I would have given it.
    You will not take pleasure in burnt offerings.
    A sacrifice to God is a broken spirit; a broken and a humbled heart God will not despise.
    Do good to Sion, Lord, in your good pleasure; and let the walls of Jerusalem be rebuilt.
    Then you will be well pleased with a sacrifice of righteousness, oblation and whole burnt offerings.
    Then they will offer calves upon your altar.
}%

\newcommand{\psalmonetwenty}{%
  I have lifted up my eyes to the mountains, from where my help will come.
  My help is from the Lord, who made heaven and earth.
  Do not let your foot waver; nor will he who guards you slumber.
  See, the One who guards Israel will neither slumber nor sleep.
  May the Lord guard you, may the Lord cover you with his right hand.
  The sun will not scorch you by day, nor the moon by night.
  May the Lord guard you from every evil; may the Lord guard your soul.
  May the Lord guard your coming in and your going out, from now and for ever more.
}