\firstletter{T}\deletechar\throughtheprayers

\heavenlyking
\footnote{\alt{The prayer,} \textbf{Heavenly King} \alt{is not said from Pascha until Pentecost. From Pascha until Leavetaking, instead say }\textbf{Christ is risen from the dead...} \alt{three times.}}

\prayer{The Trisagion Prayers}

\trisagion\\

\comeletusworship

\prayer{Psalm 50}

\psalmfifty

\prayer{Psalm 69}

O God, come to my help; Lord, hasten to help me. Let those who seek my soul be shamed and confounded.
Let those who wish me evil be turned back and put to shame.
Let those who say to me, 'Good, good!' be turned back immediately, ashamed.
Let all who seek you, O God, be glad and rejoice in you.
Let all who love your salvation ever say: 'The Lord be magnified.'
But I am poor and needy; help me, O God. You are my helper and my deliverer; Lord, do not delay.

\prayer{Psalm 142}

Lord, hear my prayer: in your truth give ear to my supplication, and in your righteousness hear me.
Do not enter into judgement with your servant: for in your sight no one living can be justified.
For the enemy pursued my soul, humbled my life to the ground.
Made me dwell in darkness, like those for ever dead.
My spirit grew despondent within me and my heart within me was troubled.
I remembered days of old, I meditated on all your works: I made the works of your hands my meditation.
I stretched out my hands towards you: my soul thirsted for you like a waterless land.
Hear me swiftly, O Lord, my spirit has failed.
Do not turn your face from me, or I shall be like those who go down to the Pit.
Make me hear of your mercy in the morning, for I have hoped in you.
Make known to me the way in which I should walk, for to you I have lifted up my soul.
Deliver me from my enemies, Lord: I have run to you for shelter.
Teach me to do your will, for you are my God.
Your good Spirit will guide me in an upright land.
For your name's sake, O Lord, you will give me life.
In your justice, you will bring my soul out of trouble, in your mercy slay my enemies,
and destroy all those that afflict my soul, for I am your servant.

\prayer{The Little Doxology}

\smalldoxology{night}

\prayer{The Symbol of Faith}

\creed

\prayer{To the Mother of God}

It is truly right to call you blessed, who gave birth to God,
ever-blessed and most pure and the Mother of our God.
\greaterinhonour

\prayer{The Trisagion Prayers}

\trisagion

\prayer{Apolytikia}

God of our fathers, who always deal with us in your forbearance,
do not withdraw your pity from us, but at their intercessions guide our life in peace.

Your Church, clothed throughout the world as in purple and fine linen with the blood of your Martyrs,
cries out to you through them: Christ, our God, send down your mercy on your people;
give peace to your city and to our souls your great mercy.

\textit{\glory.}

With the Saints, O Christ, give rest to the souls of your servants,
where there is neither sickness, nor sorrow, nor sighing, but life without end.

\textit{\bothnow.}

Through the intercession of all the Saints and of the Mother of God,
give us your peace, Lord, and have mercy on us, for you alone are merciful.
\footnote{But if it is the season of a Great Feast, instead read the Kontakion of the Feast.}

\mercy{40}

\prayer{The Prayer of the Hours}

\hours

\mercy{3}

\glorybothnow

\greaterinhonour

\throughtheprayers

\mercy{12}

And save and help us, All-holy Virgin.

\prayer{Prayer to the Mother of God}

Spotless, undefiled, incorrupt, immaculate, pure Virgin, Bride of God and Lady,
who by your marvellous conceiving united God the Word with mankind and joined our
rejected human nature to the heavenly realm; the only hope of the hopeless,
help of the attacked, ready assistance of those who flee to you, and refuge of all Christians;
do not turn in loathing from me, an accursed sinner,
who have made myself utterly worthless through shameful thoughts and words and deeds,
and through the sloth of the pleasures of life have become a slave to my own will.
But as Mother of the God who loves mankind have compassion on me, a sinner and a prodigal,
in your love for mankind, and accept the prayer I offer you from polluted lips.
And using your Mother's boldness, implore your Son, our Master and Lord,
that He open to me also the compassionate heart of his goodness,
and disregarding my countless offences turn me back to repentance,
and make me a tried worker of his commandments. And, as you are full of mercy,
compassion and loving-kindness, be ever near me: in this present life a fervent helper and protector,
shielding me from the enemy's assaults and guiding me to salvation,
and at the moment of my departure watching over my wretched soul
and driving far from her the dark forms of evil demons;
but on the dread day of judgement, delivering me from eternal punishment
and making me heir to the ineffable glory of your Son and our God.
All this may I obtain, my Lady, most holy Mother of God, through your mediation and assistance;
through the grace and love for mankind of your only-begotten Son,
our Lord and God and Saviour, Jesus Christ. To whom are due all glory, honour and worship,
with his Father who is without beginning and his all-holy, good and life-giving Spirit,
now and for ever, and to the ages of ages. Amen.

\prayer{Prayer to Our Lord Jesus Christ}

And grant us, Master, as we go to our sleep, rest of body and soul;
and guard us from the gloomy sleep of sin and from every dark pleasure of the night.
Calm the assaults of the passions, quench the fiery arrows of the evil one that are cunningly aimed at us;
put down the rebellions of our flesh and still our every earthly and material thought.
And grant us, O God, a watchful mind, chaste thought, a wakeful heart,
sleep that is light and free from every satanic fantasy.
Rouse us at the time for prayer strengthened in your commandments,
and holding firmly within us the memory of your judgements.
Grant that we may sing your glory all night long, and so hymn,
bless and glorify your all honoured and majestic name, of Father,
Son and Holy Spirit, now and for ever, and to the ages of ages. Amen.

\prayer{To the Mother of God}

Most glorious, ever-virgin, blessed Mother of God, offer our prayer to your Son and our God,
and ask that through you he may save our souls.

\prayer{Prayer of Saint Joannicius}

The Father is my hope, the Son my refuge, the Holy Spirit my protection. Holy Trinity, glory to you.

\prayer{To the Mother of God}

All my hope I place in you, Mother of God, guard me under your protection.

Because of you, O Full of grace, all creation rejoices, the ranks of Angels and the human race;
hallowed Temple and spiritual Paradise, pride of Virgins;
from you God was incarnate and he, who is our God before the ages, became a little child.
For He made your womb a throne and caused it to become wider than the heavens.
Because of you, O Full of grace, all creation rejoices; glory to you.

\prayer{Prayer to the Gaurdian Angel}

Holy Angel, overseer of my wretched soul and miserable life, do not abandon me a sinner,
do not desert me because of my inconstancy;
leave no place for the evil demon to obtain dominion over me by gaining control of this mortal body;
strengthen my wretched and feeble hand, and guide me into the way of salvation.
Yes, Holy Angel of God, guardian and protector of my wretched soul and body,
pardon me all the things by which I have distressed you all the days of my life,
and whatever sins I have committed to-day; 
shelter me in the coming night and protect me from every abuse of the adversary,
that I may not anger my God by any sin; and intercede for me to the Lord,
to strengthen me in his fear, and show me to be a worthy servant of his goodness. Amen.

\prayer{To the Mother of God}

To you my Champion and Commander I your city, saved from disasters, dedicate,
O Mother of God, hymns of victory and thanksgiving; but as you have unassailable might,
from every kind of danger now deliver me, that I may cry to you: Hail, Bride without bridegroom!

Most Holy Mother of God, save us.

\prayer{The Angelic Salutation}

Virgin, Mother of God, Hail, Mary full of grace, the Lord is with you;
blessed are you among women, and blessed is the fruit of your womb,
for you have given birth to the Saviour of our souls \alt{(x3)}.

\prayer{Dismissal}

\glorybothnow

\mercy{12}

\prayer{Apolytikion. Tone 3}

Awed by the beauty of your virginity and by the splendour of your purity,
Gabriel cried aloud to you, Mother of God: 
How can I praise you as I should? By what name shall I invoke you? I am troubled and amazed.
Therefore, as I was commanded, I cry to you: Hail, full of grace!\\

\throughtheprayers

